---
title: A template document
author: 
- name: Author 1
  affiliation: Department of text editors, Vim University
  email: author.1@vim.co.uk
- name: Author 2
  affiliation: Department of text editors, The Emacs Institute
  email: author.2@emacs.co.uk
date: 21 October, 2015
biblio-files: my-refs
abstract: |
  This is the abstract of a template document which can be edited. The content of this document can be modified and added to as necessary. It provides examples of how to handle maths, tables, data analysis and images when making a document using knitr.
---

<!--
Notes can be added in the source code of the Rmd file.
-->

```{r Setup, include=FALSE, results="hide", warning=FALSE}
opts_chunk$set(fig.path = "figures/", dev=c("cairo_pdf"), fig.pos='htbp', fig.width=5, fig.height=2, dpi=700, fig.show='hold', fig.lp="fig:", cache=TRUE, par=TRUE, echo=FALSE, results="hide", message=FALSE, warning=FALSE)

library(extrafont)
font_import(pattern="LinBiolinum")
```

# Introduction

The text in this document can be replaced. This document's source code (`paper.Rmd`) is available at \url{https://github.com/tomravalde/workflow}, along with the scripts and dependencies required to build the PDF. The GitHub repository provides the requirements and instructions in order to be able to produce this document and others like it. This workflow is based on that described in @Healy2014 and uses Markdown, LaTeX, R, the knitr R-package [@knitr2015] and pandoc [@MacFarlane2014].

# Maths

You can mix and match Markdown with \LaTeX syntax, for example for mathematical typesetting as in Equation \eqref{eq:pythag}:

\begin{align}
a^2 = b^2 + c^2.
\label{eq:pythag}
\end{align}

# Tables

When typesetting tables (such as Table \ref{tab:text-editors}), I like to use the `xtable` function (from the `xtable` R package). This allows you to create your table in a spreadsheet which you then save as a CSV file (see `text-editors.csv`).

```{r table-text-editors, results="asis"}
library(xtable)

table.csv <- read.csv("text-editors.csv")
table.tex <- xtable(table.csv, caption = "The differences between vi and Emacs, from Wikipedia (\\url{http://en.wikipedia.org/wiki/Editor_war}).\\label{tab:text-editors}", align="llp{7cm}p{7cm}")

print(table.tex,
      size = '\\small',
      floating.environment='sidewaystable',
      comment = FALSE,
      booktabs = TRUE,
      include.rownames = FALSE,
      sanitize.text.function = identity)
```

# Processing and presenting data with knitr

By the magic of knitr, data can be processed and presented using the same source code as the rest of the document's content. An example is given in Figure \ref{fig:google-fight}.

```{r google-fight, fig.height = 3, fig.cap = "\\label{fig:google-fight}Google fights results."}
library(ggplot2)

# Define theme for all plots
theme_tom  <- theme_bw() +
  theme(text = element_text(family = "Linux Biolinum"),
	legend.position="top")

fight <- read.csv("vim-emacs-google.csv")

ggplot(fight, aes(Editor, Hits/1e6)) +
  theme_tom +
  geom_bar(stat = "identity") +
  ylab("Hits (millions)") +
  theme(axis.title.x = element_blank())
```

# Images

Unfortunately, using Markdown to specify a figure size in a PDF is near-impossible. So for figures, I use standard \LaTeX code, as for Figure \ref{fig:xkcd-text-editors}.

\begin{figure}[htbp]
        \centering
        \includegraphics[width=1\textwidth]{img/real_programmers.png}
        \caption{Text editors according to XKCD (\url{http://xkcd.com/378/).}}
        \label{fig:xkcd-text-editors}
\end{figure}
